\section{Weaving Semantics}

With the help of utility functions described above,We conclude 5 rules in the operational semantics of static pointcuts  based on aspectj and JVMLI. 
\subsection{Neither Advice Applicable}
This rule of the semantics describes the case where the instruction in the method m at the program counter pc is not a shadow or the advice list is empty(all the advices have been treated for this instruction). In such cases, the
current instruction is skipped and the list of advices is reset to its initial value (all the advices of the environment).
$$\frac{(\texttt{isBeforeShadow}(m,pc)\wedge \texttt{isAfterShadow}(m,pc))\vee ads=[\;]}
{\langle\xi,m,pc,ads,nextpc\rangle\longrightarrow\langle\xi,m,\xi.advices,nextpc+1\rangle}$$

\subsection{Before Advice not Applicable}
This rule fires in the case where the head of the advice list is a Before advice but is not applicable to the current instruction. This advice is then re-moved and we reconsider the possibility of weaving the same instruction with
the remaining list of advices.

$$\frac{\texttt{head(ads).kind=before}\wedge \neg \texttt{isBeforeAdviceApplicable}(\xi,m,pc,\texttt{head}(ads))}
{\langle\xi,m,pc,ads,nextpc\rangle\longrightarrow\langle\xi,m,tail(ads),nextpc\rangle}$$

\subsection{Before Advice Applicable}
This rule of the semantics represents the case where the head of the
advice list is a Before advice and is applicable to the current instruction. In
this case, the method and the environment are changed because of the Before
advice merging. The program counter of the current instruction will change also
because of the Before advice injection.Denote\\
 $beforeApplicable:=\texttt{head(ads).kind=before}\wedge \texttt{isBeforeAdviceApplicable}(\xi,m,pc,\texttt{head}(ads))$
$$\frac{beforeApplicable\wedge (\xi^\prime,m^\prime,pc^\prime)=\texttt{insertBeforeAdvice}(\xi,m,pc,\texttt{head}(ads))}
{\langle\xi,m,pc,ads,nextpc\rangle\longrightarrow\langle\xi^\prime,m^\prime,pc^\prime,\texttt{tail}(ads),pc^\prime+1}$$

\subsection{After Advice not Applicable}
This rule depicts the case where the head of the advice list is an After
advice but is not applicable to the current instruction. The head of the advice list
is then removed and we reconsider the possibility of weaving with the remaining
list of advices.
$$\frac{\texttt{head(ads).kind=after}\wedge \neg \texttt{isAfterAdviceApplicable}(\xi,m,pc,\texttt{head}(ads))}
{\langle\xi,m,pc,ads,nextpc\rangle\longrightarrow\langle\xi,m,tail(ads),nextpc\rangle}$$

\subsection{Before Advice Applicable}
This rule of the semantics represents the case where the head
of the advice list is an After advice and is applicable to the current instruction.
In this case, the method and the environment are changed because of the After
advice merging. The program counters of the current instruction and next instruction will change also because of the After advice injection.\\
 $afterApplicable:=\texttt{head(ads).kind=after}\wedge \texttt{isAfterAdviceApplicable}(\xi,m,pc,\texttt{head}(ads))$
$$\frac{afterApplicable\wedge (\xi^\prime,m^\prime,pc^\prime)=\texttt{insertAfterAdvice}(\xi,m,pc,\texttt{head}(ads))}
{\langle\xi,m,pc,ads,nextpc\rangle\longrightarrow\langle\xi^\prime,m^\prime,pc^\prime,\texttt{tail}(ads),pc^\prime+1}$$

